---
title: "Coranavirus Beliefs"
author: "Daniel Allington"
date: "2026-03-12"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(readr)
library(ggplot2)

options(scipen = 999)

d_coronavirus <- read_csv(
  '../data/life-under-lockdown-wave2-extract.csv')
```

# Hypotheses
H1 Gender is associated with number of conspiracy beliefs about coronavirus

H2 Age is associated with number of conspiracy beliefs about coronavirus

H3 Reliance on Facebook for knowledge of coronavirus is associated with number of conspiracy beliefs about coronavirus

# Findings
## Hypothesis 1
```{r}
d_coronavirus %>%
  group_by(
    gender
  ) %>%
  summarise(
    n = n(),
    Mdn = median(beliefs),
    M = mean(beliefs),
    SD = sd(beliefs)
  )
```

```{r}
d_coronavirus %>%
  filter(gender != 'In another way') %>%
  t.test(beliefs ~ gender, data = .)
```

Males in the sample believed in more conspiracy theories than females, but this was not statistically significant, t(494.31) = -1.201, p = .230.

## Hypothesis 2
```{r}
d_coronavirus %>%
  ggplot(
    aes(x = age, y = beliefs)
  ) +
  geom_jitter()
```

```{r}
d_coronavirus %>%
  cor.test(
    ~ beliefs + age,
    data = .
  )
```

There is a weak negative correlation between age and number of conspiracy beliefs, r(498) = -.24, p < .001.

## Hypothesis 3
```{r}
knowledge_levels <- c(
  'Nothing at all',
  'Not very much',
  'A fair amount',
  'A great deal'
)

d_coronavirus <- d_coronavirus %>%
  mutate(
    know_facebook = know_facebook %>%
      ordered(
        levels = knowledge_levels
      ),
    know_facebook_coded = know_facebook %>%
      as.numeric
  )

d_coronavirus %>%
  ggplot(
    aes(
      x = know_facebook,
      y = beliefs
    )
  ) +
  geom_violin()
```

```{r}
d_coronavirus %>%
  cor.test(
    ~ beliefs + know_facebook_coded,
    data = .,
    method = 'spearman'
  )
```

There is a weak positive correlation between reliance on Facebook for knowledge of coronavirus and number of conspiracy beliefs about coronavirus, rs(498) = .23, p < .001.

